03 Data Vizualization

### 2022-05-13 03_data_viz.Rmd
dF plot now PASSING

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

@@

# Load sourced functions

@@

# Setup

@@

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  filter(inc_time_d == 7) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  group_by(terrain, inc_time_d) %>% 
  summarize(terrain = terrain,
            gen_d_weighted = gen_d_weighted) %>% 
  unique() %>% 
  ggplot(aes(x = terrain,
             y = gen_d_weighted,
             fill = terrain)) +
  geom_col(width = 0.5) +
  scale_fill_manual(values = terrain_fill_swatch) +
  labs(x = "Soil Type",
       y = "Community Generation Time (d)",
       caption = "Generation time weighted by compound relative abundance") +
  theme_classic() +
  theme(legend.position = "none")
p_gen_time_mean
```

## dF and turnover plot

```{r}
p_dF <- turnover_summarized %>% 
  filter(time_course == "0d -->") %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF, dF_weighted),
    values_to = "dF", 
    names_to = "type"
  ) %>% view()

  ggplot(
    aes(
      x = inc_time_d,
      y = dF
    )
  ) +
  # Weighted data here:
  geom_line(aes(
    x = inc_time_d,
    y = dF,
    color = terrain),
    size = 1.5,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      x = inc_time_d,
      y = dF,
      color = terrain,
      fill = terrain),
    size = 2,
    alpha = 0.5
    ) +
  # Unweighted data here:
  geom_borderline(
    data = turnover_summarized,
    aes(group = compound),
    color = "gray"
) +
  geom_point(
    data = turnover_summarized,
    size = 2,
    alpha = 0.5
    ) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(
    xlim = c(0, 8),
    clip = "off"
    ) +
  facet_wrap(vars(terrain),
             nrow = 1) +
  labs(x = "Incubation Time (Days)",
       y = TeX("$ \\Delta ^2H$ (at%)"),
       ) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))

p_dF
```

```{r 2H_plots}

peaks_mapped_summarized_wppm <- turnover_summarized %>% 
    mutate(
      at2H_ppm = calibrated_at2H_without_memory * 10000,
      at2H_ppm_mc = calibrated_at2H_with_memory_correction * 10000,
      at2H_mn_zero_ppm = at2H_mn_zero * 10000,
      at2H_weighted_ppm = at2H_weighted * 10000)

p_conifer_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Gordon Gulch Conifer Forest") %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = conifer_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = conifer_color,
             size = 3,
             alpha = 0.5) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Conifer Forest") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_conifer_2H

p_grassland_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Marshall Mesa Grassland") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                      y = at2H_weighted_ppm),
                      color = grassland_color,
                  size = 1.5) +
  geom_point(aes(x = inc_time_d,
                 y = at2H_weighted_ppm), 
                 color = grassland_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Grassland") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_grassland_2H

p_tundra_2H <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Niwot Ridge Tundra") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = tundra_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = tundra_color,
                fill = tundra_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Tundra") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_tundra_2H
```

```{r}

p_tundra_2H_3d <- peaks_mapped_summarized_wppm %>% 
  filter(terrain == "Niwot Ridge Tundra") %>% 
  mutate(compound = forcats::fct_reorder(compound, rt)) %>% 
  ggplot(aes(x = inc_time_d,
             y = at2H_ppm,
             group = compound)) +
  geom_borderline(color = "gray") +
  geom_point(size = 2,
             alpha = 0.5) +
  geom_borderline(aes(x = inc_time_d,
                y = at2H_weighted_ppm),
                color = tundra_color,
            size = 1.5) +
  geom_point(aes(x = inc_time_d,
                y = at2H_weighted_ppm), 
                color = tundra_color,
                fill = tundra_color,
             size = 3) +
  scale_x_continuous(breaks = c(0, 1,2,3,4,5,6,7)) +
  coord_cartesian(xlim = c(0, 8), ylim = c(0, 1300), clip = "off") +
  labs(x = "Incubation Time (Days)",
       y = TeX("$^2H$ (ppm)"),
       title = "Tundra") +
  theme_classic() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_tundra_2H
```

>>>>

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries

@@

## Load sourced functions

@@

@@

## (PASSING) Memory effect on gen_d

```{r mean_generation_time}
p_gen_time_mean <- turnover_weighted %>% 
  select(c(terrain, inc_time_d, gen_d_weighted, gen_d_mc_weighted)) %>% 
  pivot_longer(cols = c(gen_d_weighted, gen_d_mc_weighted),
               values_to = "gen_d",
               names_to = "type") %>% 
  filter(inc_time_d == 7) %>% 
  mutate(terrain = case_when(
    terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
    terrain == "Marshall Mesa Grassland" ~ "Grassland",
    terrain == "Niwot Ridge Tundra" ~ "Tunrda" )) %>% 
  # group_by(terrain, inc_time_d) %>% 
  # summarize(terrain = terrain,
  #           gen_d_weighted = gen_d_weighted) %>% 
  # unique() %>% 
  # Plot it
  ggplot(aes(x = terrain,
             y = gen_d,
             fill = type)) +
  geom_col(width = 0.5,
           position = "dodge") +
  scale_fill_tron() +
  labs(x = "Soil Type",
       y = "Weighted Mean Generation Time (d)") +
  theme_classic() +
  theme()
p_gen_time_mean
```

## (PASSING) dF plot
Using memory-corrected values

```{r}
p_dF <- turnover_summarized %>% 
  filter(
    time_course == "0d -->",
    compound %nin% c("H2", "20:0", "22:0", "24:0", "a-15:0")) %>% 
  ungroup() %>% 
  select(terrain, inc_time_d, compound, dF_mc, calibrated_at2H_with_memory_correction_se) %>%
  left_join(
    turnover_weighted %>% 
      select(terrain, inc_time_d, dF_weighted_mc), 
    by = c("terrain", "inc_time_d")) %>% 
  group_by(
    terrain,
    inc_time_d
  ) %>% 
  pivot_longer(
    cols = c(dF_mc, dF_weighted_mc),
    values_to = "dF", 
    names_to = "type"
  ) %>% 
  mutate(compound = case_when(
    type == "dF_weighted_mc" ~ "Weighted Mean",
    TRUE ~ compound
  )) %>%
  mutate(
    terrain = case_when(
      terrain == "Gordon Gulch Conifer Forest" ~ "Conifer Forest",
      terrain == "Marshall Mesa Grassland" ~ "Grassland",
      terrain == "Niwot Ridge Tundra" ~ "Tunrda"
  )) %>%

  ggplot(
    aes(
      x = inc_time_d,
      y = dF * 10000, # convert from at% to ppm
      group = compound,
      color = terrain,
      fill = terrain,
      alpha = type,
      size = type
    )
  ) +
  geom_point() +
  geom_line() +
  facet_wrap(vars(terrain)) +
  scale_color_manual(values = terrain_color_swatch) +
  scale_fill_manual(values = terrain_fill_swatch) +
  scale_alpha_discrete(range = c(0.2, 1)) +
  scale_size_discrete(range = c(0.75, 1.25)) +
  theme_classic() +
  labs(
    x = "Time elapsed (d)",
    y = TeX("$ \\Delta ^2H$ (ppm)")
  ) +
  theme(legend.position = "none",
        strip.background = element_blank(),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_text(size = 10))
p_dF

## Turnover plot
